manuscript_notes

### 2024-10-23 notes/manuscript_notes.Rmd
update notes and supps
update ms. and notes

@@

-> I removed the code that lists priors. I kept the model code for M1, and the model formula for models M2 to M4.

@@

-> to do.

@@

>>>>

-> Still to do... It does not seem straightforward to place apa tables side by side. For now, I kept them separate and placed text between them.

@@

-> I removed the code that lists priors. I kept the model code for M1, and the model formulas for models M2 to M4.

@@

-> to do. Which intervals should we plot for the frequentist approach?

@@

# 23 oktober 2024

Still to do:
- combine tables showing person-trial and person-trial-period data sets.

- REF for time-to-death (line 127 in ms.)

- REF for reviews and tutorials on EHA (line 140)

- REF for regression (line 145)

- change paragraph (delete it and refer to suppl. material?), and add error bars to Figure 2? (line 162)

- update section 3 and add REFs (line 200-215)

- REF sampling bias (line 332)

- REF for package MASS (line 665)

- REF for prevalence (line 710)

-frequentist versus Bayesian plot: which intervals should we plot for the frequentist model?

- summary of steps involved in tutorials
